SPIDERMAN: an open source code to model phase curves and secondary eclipses.

### 2017-07-20 ms.tex
Update on Overleaf.

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[T. Louden, L. Kreidberg]{Tom Louden$^{1}$\thanks{E-mail: t.m.louden@warwick.ac.uk} and Laura Kreidberg$^{2}$\\
$^{1}$Department of Physics, University of Warwick, Coventry, CV4 7AL, UK\\
$^{2}$Department of Astronomy, Harvard University, Cambridge, MA 02138, USA}

@@

There appear to be, broadly, two classes of exoplanet atmospheres with regards to heat transport. Hot Jupiters like HD\,189733b with, relatively temperatures have highly significant hotspot offsets and efficient day-night redistribution (cite examples other than HD 189). $\mu$ Andromedae, HD\,179949b and HD\,209458b are all significantly hotter than HD\,189733b and display much higher temperature contrasts between the day and night sides, implying inefficient redistribution of energy. \citep{Harrington2006,Cowan2007,zellem2014}.

This behaviour has been anticipated in models (cite thad komacek?)

@@

A completely non-physics dependent model is a sum of spherical harmonics. This has been used before by ((cite)) an example generated by \textsc{spiderman} is displayed in figure \ref{fig:harmonics}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[T. Louden, L. Kreidberg]{Tom Louden$^{1}$\thanks{E-mail: t.m.louden@warwick.ac.uk} and Laura Kreidberg$^{2}$\\
$^{1}$Department of Physics, University of Warwick, Coventry, CV4 7AL, UK\\
$^{2}$Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}

@@

There appear to be, broadly, two classes of exoplanet atmospheres with regards to heat transport. Hot Jupiters like HD\,189733b with, relatively low temperatures have highly significant hotspot offsets and efficient day-night redistribution \citep{Knutson2007b}. $\mu$ Andromedae, HD\,179949b and HD\,209458b are all significantly hotter than HD\,189733b and display much higher temperature contrasts between the day and night sides, implying inefficient redistribution of energy. \citep{Harrington2006,Cowan2007,zellem2014}.

This behavior can be explained with the results of General Circulation Models \citep{Komacek2015,Komacek2016}

@@

A useful and non-physics dependent model is a sum of spherical harmonics. This method was used for the case of the phase curve of HD\,189733b by \citet{Majeau2012}. An example map generated by \textsc{spiderman} is displayed in figure \ref{fig:harmonics}. The main observational features of a phase curve, including the offset hotspot can typically be recovered with a only the first spherical harmonic, with the centre offset from the substellar point. \citep{Cowan2016} explore the effects of odd harmonics in phase curve data, and find that these correspond to weather features in the planet atmosphere.
